% $Id: acknowledgements.tex 1695 2015-07-23 02:10:46Z lv39 $
% $URL: https://forge.cornell.edu/svn/repos/lv39_papers/SynLBD/text/JSM2015/acknowledgements.tex $

Vilhuber acknowledges support through NSF Grants SES-1042181 and BCS-0941226. We thank 
Jorgen Harris for 
able research assistance.
This project would not have been feasible without  repeated input from Saki Kinney and Jerry 
Reiter, and their valuable work on the Synthetic LBD. 
%
\textit{Disclaimer.}
All authors were affiliated with the U.S. Census Bureau, Center for Economic Studies, when 
originally contributing to the contents of this paper. 
This document reports the results of research and analysis
undertaken by U.S. Census Bureau staff. It has undergone a Census
Bureau review more limited in scope than that given to official Census
Bureau publications. This document is released to inform interested
parties of ongoing research and to encourage discussion of work in
progress. All results have been reviewed to ensure that no confidential information is
disclosed. The views expressed herein are attributable only to the
authors and do not represent the views of the U.S. Census Bureau. 
%
\textit{Data access.}
The data used in this paper is restricted-access, and can be accessed either through the Federal 
Statistical Research Data Centers (LBD) or through the Synthetic Data Server at Cornell University 
(Synthetic LBD). Data and code used for the final version of this paper will be archived at the U.S. 
Census Bureau and made available upon request. 

